Title

### 2014-07-23 paper.tex
more colors

@@

% quick structure
Each change includes a \emph{commit message} which describes what is changed.
After a change is submitted to Gerrit, reviewers can give scores to it.
The scores will determine whether the change will be accepted or not.
Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.
In this paper, we use the term \emph{document} to refer to a single commit message or comment.
Fig. \ref{fig:hierarchy} shows the relation between documents.

\begin{figure}[h]
\centering
\includegraphics[width=2.5in]{hierarchy}
\caption{Relationship between documents.
Each rectangle represents a document, which may either be a commit message or a comment.}
\label{fig:hierarchy}
\end{figure}

@@

\subsubsection{Tokenizing, stop word removal and stemming}

>>>>

\begin{figure*}
\centering
\includegraphics[width=6in]{overview}
\caption{Overview of our classification method.}
\label{fig:overview}
\end{figure*}

@@

% quick structure
Each change includes a \emph{commit message} which describes what is changed.
After a change is submitted to Gerrit, reviewers can give scores to it.
The scores will determine whether the change will be accepted or not.
Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.

% overview
In our classification method,
all commit messages and comments that are human-written are converted into vectors using tf--idf algorithm.
Few comments are sampled and then classified manually for use in training and validation.
A model is created from these training data, from which useful comments can automatically be identified.
This process is illustrated in Fig.\ref{fig:overview}.

@@

\subsubsection{Tokenization, stop word removal and stemming}
